Parallelizing AdaBoost and Decision Trees

### 2015-08-07 paper.tex
paper changes

\section{Decision Trees}
Decision trees are a well-known method useful for classification which partitions the feature space into rectangular regions and gives each region the most common label among the training set points it contains. Each partition of the feature space is made along coordinate axes and done in a heirarchical way. Starting with the entire space, a line parallel to an axis divides it into two regions and then the same is done for these resulting regions. This process is repeated many times until the space is partitioned into several rectangles, like the example in Figure 1 (\cite{HTF}).
\begin{figure}
\includegraphic{dectreerect}
\end{figure}

 In that depiction, the lines drawn at $t_i$ represent the $i$th division of the space. Since each region is divided in two, this gives rise to a binary tree where each node represents a line drawn to partition the region existing before that node. The tree corresponding to Figure 1 is given in Figure 2 (\cite{HTF}).

 It is done in a heirarchical way that The feature space is partitioned along coordinate axes, which gives rise to decision. The most common way to partition the feature space is along coordinate axes.

@@

\begin{thebibliography}
\ref[no1] Yoav Freund Rob Schapire

\ref[no2] Hastie Friedman Tibshirani

\ref[no3] Mohri

\ref[no4] Wiki

\end{thebibliography}
\end{document}

>>>>

\section{Decision Trees}
Decision trees are a well-known method useful for classification which
partitions the feature space into rectangular regions and gives each region the
most common label among the training set points it contains. Each partition of
the feature space is made along coordinate axes and done in a heirarchical way.
Starting with the entire space, a line parallel to an axis divides it into two
regions and then the same is done for these resulting regions. This process is
repeated many times until the space is partitioned into several rectangles,
like the example in Figure 1 (\cite{HTF}). Each split is made to separate points of the two classes distinct classes into different regions as best as possible. Thus the two resulting rectangles will have a greater {\it purity} in comparison to the parent node. There are a .

\begin{figure}[b!]
\centering
\begin{minipage}{0.45\textwidth}
\centering
\includegraphics[width=2.5in]{partition}
\caption{space partitioned by a decision tree}
\end{minipage}\hfill
\begin{minipage}{0.45\textwidth}
\centering
\includegraphics[width=2.5in]{dectree}
\caption{decision tree}
\end{minipage}
\end{figure}

 In that depiction, the lines drawn at $t_i$ represent the $i$th division of the space. Since each region is divided in two, this gives rise to a binary tree where each node represents a line drawn to partition the region existing before that node. The tree corresponding to Figure 1 is given in Figure 2 (\cite{HTF}). As depicted in the two figures, the splitting of each node is done in a heirarchical way so that . The feature space is partitioned along coordinate axes, which gives rise to decision. The most common way to partition the feature space is along coordinate axes.

@@

%\begin{thebibliography}
%\bibitem{FS} Yoav Freund Rob Schapire

%\bibitem{HTF} Hastie Friedman Tibshirani

%\bibitem{Mohri} Mohri

%\bibitem{no4} Wiki
%\end{thebibliography}
\end{document}
